Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
nk-facets are finite

% theorems
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem*{theorem*}{Theorem}%[section]

@@

 {\it Combinatorial proof.}

@@

\vincent{Orient the flip graph. Connection to the lattice of torsion classes?}

>>>>

% theorems
\newtheorem{theorem}{Theorem}[]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem*{theorem*}{Theorem}%[section]

@@

 {\it Combinatorial proof.} By Lemma~\ref{lem:ExistenceOfDistinguishedArrows}, the number of walks in a finite face of~$\NKC$ is bounded by~$|Q_1\blossom|+s_\infty$, where~$s_\infty$ is the number of infinite straight walks (i.e. the number of oriented cycles in~$Q$).

@@
